My very cool title

### 2017-06-25 doc/manuscript/paper.tex
Computing PCA automatically, for all algo and all chr

% Title of paper
\title{Exploration of empirical Bayes hierarchical modeling for the
analysis of genome-wide association study data}

@@

\subsection{Analysing contact count data}
- compartment analysis
- extracting some relationships between counts genomic distances etc
- Extracting significant interactions using fit-HiC

Figure:
  - log-linear relationships between counts and distances.
  - significant interactions using fit-HiC ?

>>>>

% Title of paper
\title{My very cool title}

@@

\subsection{Analysing contact count data}

- Normalization
- Quality assessment
- Enrichment of counts
- Anything else?
    - Did we do a compartment analysis?
- Can we extend it?
  - Fit-Hic ?
